---
title: "team"
output: html_document
team Member: Syed Hasan and Tyler Smith
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
nrow(choco)
```
# Team Lab 2
### Problem 1
The overall number of chocolates rated is 1852


```{r}
hist(choco$Review.Date,main="Histogram by the year of review")
```

### Problem 2
For the first few years, there were some inconsistencies in the number of reviews, with 2006 through 2011 staying around 150. In the following years, there was a slight increase, until 2013 and 2014 both had close to 250 ratings, then 2015 and 2016 dipped. It is likely that the 2016 is not complete with very few ratings.


```{r}
summary(choco)
USA <- choco[choco$Company.Location == "U.S.A.",]
fr <- choco[choco$Company.Location == "France",]
ca <- choco[choco$Company.Location == "Canada",]
c(mean(USA$Rating),mean(fr$Rating),mean(ca$Rating))
par(mfrow=c(1,3))
hist(USA$Rating)
hist(fr$Rating)
hist(ca$Rating)

```

### Problem 3

The summary command shows the top three company location countries: USA, France and Canada.
Both the graphs and means showed that most of the chocolates are similarly distributed. 

### Problem 4
How do the three most commonly rated countries differ is cocoa percentage?

```{r}
c(mean(USA$Cocoa.Pct),mean(fr$Cocoa.Pct),mean(ca$Cocoa.Pct))
par(mfrow=c(1,3))
hist(USA$Cocoa.Pct)
hist(fr$Cocoa.Pct)
hist(ca$Cocoa.Pct)
```


### Problem 5
Overall, the distributions look similary. The USA seemed to have a greater percentage of chocolates between 80 and 100 percent cocoa. The USA and Canada each had their peak between 65-70 percent cocoa, while France's peak was between 70-75 percent cocoa. 

### Problem 6
The workflow went alright. We were able to push everything onto <https://github.com/smithty27/ds202_lab2.git> with ease. We collaborated on the project as well.

